An Implementation of the Active Contours without Edged model and the Logic Framework for Active contours on multi-channel images

### 2010-12-03 trunk/cs870/project/Report/Paper.tex
added more explanation to fgures

In order to make sure we correctly implemented the models, we had several evaluation criteria. Table~\ref{tab:criteria} summarizes these criteria, and explains
the goals of each. Some of these criteria apply for both models, while other apply to one or the other. For the rest of this section, we proceed by presenting
our experimental results for both models. For each model, we proceed in the order of these criteria starting with the simplest
cases, and incrementally challenging the model. Unless otherwise stated, all the segmentation was performed on a gray scale version of the original image.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg4.png}
\caption{Initial curve position not overlapping any area of the object. Top: the evolving curve (in red) over time where the first image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 131 x 131, $\phi_{0}(x,y) = - \sqrt{(x - 120)^2 + (y - 120)^2)} + 10$,
$\mu =0.01$, no reinitialization, cpu = 2.01 s, took 9 iterations.}
\label{fig:cv_eg4}
\end{figure*}

@@

In order to make sure the contour does not simply stop at the outside boundary of an object and ignore any details inside such as holes, we first tried a
simple donut example, and then tried two more complicated donut images.

@@

flowers here

>>>>

In order to make sure we correctly implemented the models, we had several evaluation criteria. Table~\ref{tab:criteria} summarizes these criteria, and explains
the goals of each. Some of these criteria apply for both models, while other apply to one or the other. For the rest of this section, we proceed by presenting
our experimental results for both models. For each model, we proceed in the order of these criteria starting with the simplest
cases, and incrementally challenging the model. Unless otherwise stated, all the segmentation was performed on a gray scale version of the original image. All
the images in the Chan-Vese model were run on a BLA COMPUTER and all the images in the Sandberg-Chan model were run on a BLA computer.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg4.png}
\caption{Initial curve position not overlapping any area of the object. Top: the evolving curve (in red) over time where the first image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 120)^2 + (y - 120)^2)} + 10$,
$\mu =0.01$, no reinitialization, cpu = 2.01 s, took 9 iterations.}
\label{fig:cv_eg4}
\end{figure*}

@@

In order to make sure the contour does not simply stop at the outside boundary of an object and ignore any details inside such as holes, we tried two donut
images. Figure~\ref{fig:cv_eg5} shows how the curve is able to detect the hole in the donut. Additionally, it is able to detect the various sprinkles on it.
We note that the bottom right boundary is not very exact, and this is because the lighting effect in the image makes the intensity of this area very close to
that of the background This is a known drawback of the Chan-Vese model since it only divides the image into two regions, and requires a big variation in
intensities for the curve to change. Another example showing this limitation is shown in Figure~\ref{fig:cv_eg7} where the flower parts with very low
intensities are not detected. Figure~\ref{fig:cv_eg6} shows that multiple holes in an image can also be successfully detected.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg5.png}
\caption{Successful detection of holes.  Top: the evolving curve (in red) over time where the first image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 131 x 131, $\phi_{0}(x,y) = - \sqrt{(x - 65.5)^2 + (y - 65.5)^2)} + 32.8$,
$\mu =0.01$, no reinitialization, cpu = 8.12 s, took 12 iterations.}
\label{fig:cv_eg5}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg6.png}
\caption{Successful detection of multiple holes.  Top: the evolving curve (in red) over time where the first image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} + 75$,
$\mu =0.01$, no reinitialization, cpu = 15.07 s, took 23 iterations.}
\label{fig:cv_eg6}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{cv_eg7.png}
\caption{Inability to detect low intensities that have not much variation from their background.  Top: the evolving curve (in red) over time where the first
image shows the initial
contour.Bottom: evolving segmentation over time until the object is detected. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} + 75$,
$\mu =0.01$, no reinitialization, cpu = 1.35 s, took 6 iterations.}
\label{fig:cv_eg7}
\end{figure*}

@@
